---
title: 'Statistics'
subtitle: 'Assignment 1: Generating plots'
author: "Brian Beadle"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: false
    lightbox: false
    gallery: false
    highlight: tango
    fig_width: 13
    fig_height: 9
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Generate the following plots using the student data, then email the ```R``` script file to me or show me in class. Refer to the second exercise on my [website](https://brianbeadle.github.io/statistics.html) if you are stuck.

Some guidelines:

- Choose colors that are different from what you see below. You can choose any that you want!
- Be sure that your first plot has a matching number of columns shown below (hint: they are ```bins```)
- Write the axis labels exactly as you see them below

```{r, echo=FALSE, out.width='100%', warning=FALSE, message=FALSE}
rm(list=ls())

library(tidyverse)   # includes dplyr, readr, tidyr, and more
library(ggplot2)     # for creating plots

d <- read.csv("student_data_complete.csv")

ggplot(d, aes(x = hand, y = after_stat(count / sum(count)))) +
  geom_histogram(bins = 8, 
                 fill = "gray", 
                 color = "black") +
  labs(y = "Relative frequency", 
       x = "Hand size (cm)")

d$pet <- as.factor(d$pet)

ggplot(d, aes(x = hand)) +
  geom_boxplot(fill = "gray", color = "black") +
  labs(x = "Hand size (cm)")
```